\section{Inter/Intra University Liaison}
\label{interintra-university-liaison}

\subsection{Hosted Conferences and Competitions}
\label{hosted-conferences-and-competitions}

\subsubsection{General}
\label{conferences-general}

\begin{enumerate}
 \item
  The McMaster Engineering Society may submit a bid to host any ESSCO/CFES-related conferences or competitions when they become available for bidding by the relevant organization.
 \item
  It is the responsibility of the VPX to form a committee to select Chair(s).
 \item
  It is the responsibility of the Chair(s) to ensure that an organizing committee is formed and active. The number of members on the committee as well as its structure is up to the discretion of the co-chairs.

\end{enumerate}

\subsection{External Conference and Competitions}
\label{external-conference-and-competitions}

\subsubsection{Open Conferences and Competitions}
\label{open-conferences-and-competitions}

\begin{enumerate}
 \item
  Open conferences and competitions are events that can be attended by McMaster undergraduate students in the Faculty of Engineering. They are considered to be open for the VPX and council to review and provide a subsidy if approved. They will be evaluated for valuable conference content and credible organization, and approval is not recurring. It must be reviewed each time the conference or competition is run. MES Groups and Teams are not eligible to apply for the Open Conferences and Competitions fund.
 \item
  Other conferences or events are considered to be open following review by the VPX. Individuals seeking subsidy must be MES members.

\end{enumerate}

\subsubsection{Delegation Selection for Open Conferences and Competitions}
\label{delegation-selection-for-open-conferences-and-competitions}

\begin{enumerate}
 \item
  A head delegate shall select a delegation to attend the conference or competition as they see fit. The delegate selection process shall be transparent, and presented to the MES Council when applying for funding before attending the conference or competition. Delegates should be selected based on appropriate criteria as defined by the conference or competition organizer.
\end{enumerate}

\subsubsection{Delegate Responsibilities}
\label{delegate-responsibilities}
\begin{enumerate}
 \item
  Delegates are expected to represent McMaster in a positive manner
 \item
  The head delegate is responsible for the following duties:

  \begin{enumerate}
   \item
    Determining travel arrangements to and from the conference
   \item
    Holding a meeting prior to the conference for all delegates
   \item
    Acquiring receipts/invoices for all delegate, transportation, and accommodation fees
   \item
    Creating a presentation for council to summarize the conference or competition, unless special considerations need to be made for confidentiality purposes
   \item
    Creating a report for publication in The Frequency and/or the MES website detailing events from the conference or competition

  \end{enumerate}
\end{enumerate}

\subsubsection{Affiliate Conferences}
\label{affiliate-conferences}
\begin{enumerate}
 \item
  Affiliate conferences are conferences that are hosted by student organizations that the MES is currently affiliated with, namely the Engineering Students Societies' Council of Ontario (ESSCO) and the Canadian Federation of Engineering Students (CFES). Any McMaster undergraduate student in the Faculty of Engineering is eligible to apply to attend Affiliate conference, except for ESSCO PM and CFES SDES. Only students who are MES members will be considered as a delegate unless they demonstrate financial need at the discretion of the VPX.
 \item
  The following are annual closed conferences officially recognized by the MES:

  \begin{enumerate}
   \item
    Engineering Student Societies' Council of Ontario Conference On Advocacy And Leadership in Engineering (ESSCO CALE)
   \item
    Engineering Student Societies' Council of Ontario President's Meeting (ESSCO PM)
   \item
    Engineering Student Societies' Council of Ontario Professional Engineers of Ontario student conference (ESSCO PEO-SC)
   \item
    Engineering Student Societies' Council of Ontario First Year Integration Conference (ESSCO FYIC)
   \item
    Canadian Federation of Engineering Students Summit on Development of Engineering Societies (CFES SDES)
   \item
    Canadian Federation of Engineering Students Canadian Engineering Leadership Conference (CFES CELC)
   \item
    Canadian Federation of Engineering Students Conference on Sustainability in Engineering (CFES CSE)
   \item
    Canadian Federation of Engineering Students Conference on Diversity in Engineering (CFES CDE)

  \end{enumerate}
\end{enumerate}

\subsubsection{Delegate Selection for Affiliate Conferences}
\label{delegate-selection-for-affiliate-conferences}
\begin{enumerate}
 \item
  The VPX shall act as head delegate to all affiliate conferences recognized by the MES when there is a vote

  \begin{enumerate}
   \item
    In the event that they cannot attend, the President or another representative will attend in their place
   \item
    For affiliate conferences that do not have a plenary or General Assembly, the Delegation Selection Committee (see MES Bylaws Section \ref{delegate-selection-committee}) will choose a replacement from the pool of interested applicants -- priority shall be considered in the following decreasing order (with conference experience being taken into account): Executive members, Council members, general members.
  \end{enumerate}
 \item
  The remainder of the delegation is to be chosen by the Delegate Selection Committee from the pool of interested applicants
 \item
  All students interested in becoming a delegate must submit an application created by the VPX.
 \item
  Delegates shall be selected according to the following criteria:

  \begin{enumerate}
   \item
    Their status as a current MES member
   \item
    Past, present, and intended future involvement with the MES and the host organization (i.e. ESSCO or CFES)
   \item
    Ability to represent McMaster as a mature and responsible student
   \item
    Involvement in extracurricular engineering-related activities
   \item
    Appropriateness for the delegate to attend based on the conference content
  \end{enumerate}
 \item
  The Delegate Selection Committee shall decide on an appropriate number of delegates to send to each conference and is to choose a delegation representative of the engineering student body (i.e. year, program, Team members).
 \item
  Conference applications shall be advertised by the VPX through appropriate channels.

\end{enumerate}

\subsubsection{Delegate Responsibilities}
\label{delegate-responsibilities-1}
\begin{enumerate}
 \item
  The delegates are all to attend different workshops at the conference, and be attentive at all sessions.
 \item
  The head delegate is responsible for the following duties:

  \begin{enumerate}
   \item
    Determining travel arrangements to and from the conference
   \item
    Collecting delegate and transportation fees.
   \item
    Holding a meeting prior to the conference for all delegates and the VPX, if the head delegate is not the VPX.
   \item
    Acquiring receipts/invoices for all delegate, transportation, and accommodation fees.
   \item
    Keeping delegates informed on their conference duties, in advance of the conference.

  \end{enumerate}
\end{enumerate}

\subsubsection{Closed Competitions}
\label{closed-competitions}
\begin{enumerate}
 \item
  Closed Competitions are conferences that are attended by invitees only. Invitations are offered based on performance at other competitions. The following annual competitions are officially recognized by the MES:

  \begin{enumerate}
   \item
    Ontario Engineering Competition (OEC)
   \item
    Canadian Engineering Competition (CEC)
  \end{enumerate}
\end{enumerate}
